A Physically Motivated Framework to Compare Merger Timescales\\ of Isolated Low- and High-Mass Galaxy Pairs Across Cosmic Time

### 2024-03-20 paper/main.tex
Updates from Overleaf

\subsubsection{Orbits} 
\begin{figure}[htb]
    \begin{center}
    \includegraphics[width=\columnwidth, trim={0.4cm 1.75cm 1cm 3.5cm}, clip]{plots/bet-on-it/5_exampleorbits.png}
    \caption{Selection of example orbits of low-mass major pairs selected at $z=1.5$, showing the separation between the primary and secondary halo of the pair as a function of lookback time. 
    (Top) Orbits of pairs that merge before $z=0$.
    (Middle) Orbits of pairs that did not merge before $z=0$ (non-mergers), but are likely to merge if the simulation continued. 
    (Bottom) Orbits of pairs that did not merge before $z=0$ (non-mergers) and are unlikely to do so in the future $\sim2\Gyr$ (past the end of the simulation).
    Solid lines represent the parts of the orbit post-infall, while the dashed lines show the pre-infall portion of the orbit before the pairs first share a common FoF group. 
    Triangle points in the first panel show the first redshift after merger where the orbit has a separation of $0\,\kpc$.
    The vertical grey line marks $z=1.5$ at a lookback time of $9.5\,\Gyr$.
    }
    \label{fig:example-orbits}
    \end{center}
\end{figure}

@@

\section{Pair Sample Properties}
\begin{figure}[htb]
    \begin{center}
    \includegraphics[width=\columnwidth]{plots/bet-on-it/6_paircount.png}
    \caption{\kc{need caption}\kc{Change redshift limits?} The number of low-mass (green) and high-mass (pink) pairs as a function of redshift. The solid lines show the number of unique pairs at a given redshift, while dashed lines show the number of unique pairs at a given redshift that will merge before $z=0$.
    For these two lines, we have only counted pairs at a given redshift if they have not merged, but have experienced first infall at a previous time. 
    \kc{I believe} The decrease in the number of unique low-mass pairs from $z=2$ to $z=0$ is due to pairs being removed from the sample due to mergers.
    %
    The thin dotted lines show the number of pairs that were selected via the pair criteria at that specific redshift. 
    }
    \label{fig:num-pairs}
    \end{center}
\end{figure}

>>>>

\subsubsection{Orbits} 
\begin{figure}[tb]
    \begin{center}
    \includegraphics[width=\columnwidth]{plots/bet-on-it/5_exampleorbits.png}
    \caption{Selection of example orbits of low-mass major pairs selected at $z=1.5$, showing the separation between the primary and secondary halo of the pair as a function of lookback time. 
    (Top) Orbits of pairs that merge before $z=0$.
    (Middle) Orbits of pairs that did not merge before $z=0$ (non-mergers), but are likely to merge if the simulation continued. 
    (Bottom) Orbits of pairs that did not merge before $z=0$ (non-mergers) and are unlikely to do so in the future $\sim2\Gyr$ (past the end of the simulation).
    Solid lines represent the parts of the orbit post-infall, while the dashed lines show the pre-infall portion of the orbit before the pairs first share a common FoF group. 
    Triangle points in the first panel show the first redshift after merger where the orbit has a separation of $0\,\kpc$.
    The vertical grey line marks $z=1.5$ at a lookback time of $9.5\,\Gyr$. \kc{state in words that the FoF group need not be common for the remainder of the orbit, but will definitely be by merger.}
    }
    \label{fig:example-orbits}
    \end{center}
\end{figure}

@@

\section{Pair Sample Properties}
\begin{figure}[htb]
    \begin{center}
    \includegraphics[width=\columnwidth]{plots/bet-on-it/6_paircount.png}
    \caption{\kc{need caption}\kc{Change redshift limits?} The number of low-mass (green) and high-mass (pink) pairs as a function of redshift. The solid lines show the number of unique pairs at a given redshift, while dashed lines show the number of unique pairs at a given redshift that will merge before $z=0$.
    For these two lines, we have only counted pairs at a given redshift if they have not merged, but have experienced first infall at a previous time. 
    \kc{I believe... think more} The decrease in the number of unique low-mass pairs from $z=2$ to $z=0$ is due to pairs being removed from the sample due to mergers.
    %
    The thin dotted lines show the number of pairs that were selected via the pair criteria at that specific redshift. 
    }
    \label{fig:num-pairs}
    \end{center}
\end{figure}
